### 2012-03-12 docs/slides/slides.tex
Work on getting dashboard and predict scripts running again.
Add material to slides.

\begin{itemize}
\item Restricts the class of effects one can use
\item Complexity of likelihood computation reduced ($N^2 \rightarrow N$)
\end{itemize}

@@

\begin{frame}{Synthetic example}
Parameter estimates

>>>>

\begin{itemize}
\item Restricts the class of effects one can use
\item Complexity of likelihood computation reduced ($N^2 \rightarrow N$)
\end{itemize}
\end{frame}

@@

\begin{frame}{Synthetic example}
True parameters

Observed counts for each block.

Parameter estimates (using Gibbs sampling for $\mathbf{z}$ and slice sampling for $\boldsymbol{\beta}$).
\end{frame}

\begin{frame}{Application: Dyadic interactions on Twitter}
  \begin{itemize}
  \item Tweets from Twitter.com occurring between from May 11, 2009 to January 26, 2012 with hashtag \texttt{\#rstats}.
  \item Selecting tweets beginning with the \texttt{@} symbol, and mark the first mentioned user as the recipient.
  \item Of 28337 total tweets in this time period, 3926 were directed events among a total of 1079 users.
  \item We consider a subset 487 users who participated in more than one event, using a training set of 2000 events and a test set of 1330 events.
  \end{itemize}
\end{frame}

\begin{frame}{Application: Dyadic interactions on Twitter}
Prediction experiments and model comparison
\end{frame}

\begin{frame}{Application: Dyadic interactions on Twitter}
Plot parameter estimates for winning model
Compare to fitting a single relational event model
\end{frame}

\begin{frame}{Discussion}
Interpretation of parameter estimates
  \begin{itemize}
  \item Method clusters with respect to the relational event dynamics for a set of actors
  \end{itemize}

Main takeaways
\begin{itemize}
\item Detailed, highly dependent model for local structure\\ (using relational event models)
\item Latent variable model to capture meso-level structure \\(using stochastic block model)
\end{itemize}
\end{frame}

\begin{frame}{Future directions}
  \begin{itemize}
  \item Benefits of mixed-membership ideas
  \item Dirichlet process instead of fixed $K$ (with split-merge sampling?)
  \end{itemize}
\end{frame}

\begin{frame}{References}
